Social Participation Ontology: community documentation, enhancements and use examples

### 2015-09-18 plosOne/plos.tex
feito esquema basico para redirecionar referenciamentos para os arquivos

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

@@

%% END MACROS SECTION

@@

\begin{itemize}
    \item Various proposals for the \vcps\ logo, some of which are in Figure~\ref{logo}.
    \item Figure~\ref{fig:v1} shows an English and completed version of the original diagram of \ops\ in the document~\cite{conceptualMod}. For completeness of exposition, the original diagram is in Appendix~\ref{ap:dia}, Figure~\ref{fig:diaorig}.
    \item A diagram for general public consultations. Given the details and the pertinence of public consultations for \ops, the digram is exposed in Appendix~\ref{ap:public} and Figure~\ref{fig:consult}.
\end{itemize}

@@

\section{Concluding remarks and future work}\label{conc}
\opsi, based in \vcps,
yields initial steps in achieving an effective social participation ontology: community has registered activities and delivered reference documents, including this article.
Sections~\ref{exp} and~\ref{ospUtil} have expansion directions for the ontology, regarding uses, further definition of classes, upper ontologies and related ontological structures.

@@

%
%\section{Upper and domain ontologies}\label{upper}
%There are various ontologies of interest for participatory democracy and thus for \ops. To exemplify, three sources were chosen:
%\begin{itemize}
%    \item DBpedia $\rightarrow$ ``a crowd-sourced community effort to extract structured information from Wikipedia''. Convenient for bootstrapping the OPS to out-of-domain knowledge with crowd-sourced structured information~\cite{dbpedia}.
%    \item W3C recommendations for open-government, these are the work product of specialized groups and are regarded in high account by the semantic web community~\cite{egovW3C}.
%    \item Current upper ontologies used in \ops: \foaf\ and \bfo.
%\end{itemize}
%
%This list is endless and further work should narrow the interest to essential upper ontologies. As part of the linkage to other participatory instances and even to other domains, this is a core 
%
\section{Restrictions in VCPS and initial OPS which were removed for the time being}\label{ap:restr}

@@

\section{Public consultation}\label{ap:public}
Public consultations have core importance in participatory democracy and the model in Figure~\ref{fig:consult} was conceived as part of \vcps\ community documentation.
An \owl\ implementation of such public consultation was meant to be developed and made public, with dedicated attention.
Considerations of this public consultation with respect to the \ops\ and formal existent instances was envisioned as well.
This public consultation model is observed here for completeness of exposition and further details goes beyond the scope of this article. A public consultations along the lines of a recent Presidential decree~\cite{decree} was formalized in \obs\ \owl\ and in \vbs\ \skos~\cite{pnud5}.

\begin{figure*}[H]
    \centering
%    \includegraphics[width=0.9\textwidth]{figs/publicConsultation__}
    \caption{A diagram representation of a general public consultation, part of initial \vcps\ documentation. Further context of this image is in Appendix~\ref{ap:public}.}
    \label{fig:consult}
\end{figure*}

>>>>

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}
\hypersetup{
        colorlinks,
        linkcolor={red!50!black},
        citecolor={blue!50!black},
        urlcolor={blue!80!black}
}

@@

%% END MACROS SECTION
\usepackage{xr}
\externaldocument{SI/S3original}
\externaldocument{SI/S4consultation}
\usepackage[section] {placeins}

@@

\begin{itemize}
    \item Various proposals for the \vcps\ logo, some of which are in Figure~\ref{logo}.
%    \item Figure~\ref{fig:v1} shows an English and completed version of the original diagram of \ops\ in the document~\cite{conceptualMod}. For completeness of exposition, the original diagram is Supporting Information Figure~\ref{fig:diaorig}.
    \item A diagram for general public consultations. Given the details and the pertinence of public consultations for \ops, the digram is exposed in Supporting Information Figure~\ref{fig:consult}.
\end{itemize}

@@

\section{Concluding remarks}\label{conc}
\opsi, based in \vcps,
yields initial steps in achieving an effective social participation ontology: community has registered activities and delivered reference documents, including this article.
Sections~\ref{exp} and~\ref{ospUtil} have expansion directions for the ontology, regarding uses, further definition of classes, upper ontologies and related ontological structures.

@@

%
%\section{Upper and domain ontologies}\label{upper}
%There are various ontologies of interest for participatory democracy and thus for \ops. To exemplify, three sources were chosen:
%\begin{itemize}
%    \item DBpedia $\rightarrow$ ``a crowd-sourced community effort to extract structured information from Wikipedia''. Convenient for bootstrapping the OPS to out-of-domain knowledge with crowd-sourced structured information~\cite{dbpedia}.
%    \item W3C recommendations for open-government, these are the work product of specialized groups and are regarded in high account by the semantic web community~\cite{egovW3C}.
%    \item Current upper ontologies used in \ops: \foaf\ and \bfo.
%\end{itemize}
%
%This list is endless and further work should narrow the interest to essential upper ontologies. As part of the linkage to other participatory instances and even to other domains, this is a core 
%
\section{Restrictions in VCPS and initial OPS which were removed from current OPS}\label{ap:restr}

@@

%\section{Public consultation}\label{ap:public}
%Public consultations have core importance in participatory democracy and the model in Figure~\ref{fig:consult} was conceived as part of \vcps\ community documentation.
%An \owl\ implementation of such public consultation was meant to be developed and made public, with dedicated attention.
%Considerations of this public consultation with respect to the \ops\ and formal existent instances was envisioned as well.
%This public consultation model is observed here for completeness of exposition and further details goes beyond the scope of this article. A public consultations along the lines of a recent Presidential decree~\cite{decree} was formalized in \obs\ \owl\ and in \vbs\ \skos~\cite{pnud5}.
%
%\begin{figure*}[H]
%    \centering
%%    \includegraphics[width=0.9\textwidth]{figs/publicConsultation__}
%    \caption{A diagram representation of a general public consultation, part of initial \vcps\ documentation. Further context of this image is in Appendix~\ref{ap:public}.}
%    \label{fig:consult}
%\end{figure*}
